Measurement Clusterization in Bayesian D-optimal Designs in Infinite Dimensions

### 2024-07-25 latex/prelims.tex
Before dropping spacebars in labels

The connection between parameter and observation spaces is made by the
\emph{forward operator} \(\fwd: \hilp \to \hilo\). We assume the
forward operator \(\fwd\) is linear. In the inverse problem of the 1D
heat, the forward operator is determined by the time evolution of the
1D heat equation \eqref{eq:heat1} and \eqref{eq:heat2}.

>>>>

The connection between parameter and observation spaces is made by the
\emph{forward operator} \(\fwd: \hilp \to \hilo\). We assume the
forward operator \(\fwd\) is linear. In the inverse problem of the 1D
heat equatin, the forward operator is determined by the time evolution
of the 1D heat equation \eqref{eq:heat1} and \eqref{eq:heat2}.
